---
title: "scraper"
author: "Sosaria Unbound"
date: "11/30/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include = FALSE)
```

## DNDBeyond Character and Campaign Scraper Experiments

```{r package_installation}
install.packages(c("stringr", "tibble", "RSelenium", "rvest"))
```

```{r load_libraries}
library(stringr)
library(tibble)
library(RSelenium)
library(rvest)
```

Much of this code was taken from Leslie Myint's dndscraper project over here: https://github.com/lmyint/dnd_analysis -- I would encourage you to check it out. Her scraper runs through all the monsters and pulls them down.


First thing's first, get the login working. 

```{r define_url}
url <- "https://www.dndbeyond.com/login"
```

Next we setup the RSelenium driver. You should have a robot controlled chrome window open up.

```{r setup_rselenium_driver}
rd <- rsDriver(browser = "chrome")
rem_dr <- rd[["client"]]
```

After that, run this to navigate to the URL and get to the twitch login.

```{r navigate_login}
rem_dr$navigate(url)
rem_dr$findElement(using = "css selector", value = ".twitch-button")$clickElement()
```

*Manually enter your credentials here and hit login* Run the following script to have it click authorize.

```{r authorize_login}
rem_dr$findElement(using = "css selector", value = ".js-authorize-text")$clickElement()
```

Next we're setting up the campaigns URL.

```{r}
rem_dr$navigate("https://www.dndbeyond.com/campaigns")
```

The following finds all of the campaign ID's of your active campaigns. 

```{r}
page <- read_html(rem_dr$getPageSource()[[1]])

campaign_ids <- page %>%
  html_nodes(".ddb-campaigns-list-item-footer-buttons-item") %>% 
  html_attr("href") %>%
  str_extract(string = ., pattern = "\\d+") %>%
  unique()
```

Next, we loop through the campaigns and get all of the character_page ID's.

```{r}
character_pages <- 0
for (i in 1:length(campaign_ids)) {
  
rem_dr$navigate(paste("https://www.dndbeyond.com/campaigns/", campaign_ids[i], sep = ""))
campaign_page <- read_html(rem_dr$getPageSource()[[1]])

cp <- campaign_page %>%
  html_nodes(".ddb-campaigns-character-card-footer-links-item-view") %>%
  html_attr("href")

character_pages <- c(character_pages, cp) 
}
```

We then loop through the character_page ID's and retrieve all of the stats for each character.

```{r}
character_pages <- character_pages[2:length(character_pages)]

for (i in 1:length(character_pages)) {
  rem_dr$navigate(paste("https://www.dndbeyond.com", character_pages[i], sep = ""))
  Sys.sleep(7)
  cp <- read_html(rem_dr$getPageSource()[[1]])
  cp %>%
    html_nodes(".ct-ability-summary__secondary") %>%
    html_text() -> t
  
  print(t)
}
```

